Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-10 paper/main_4.1_cnn_for_eads.tex
revise section headers
remove extra spacing

% Results and Discussion Part One: Adsorption energy prediction from eDOS with CNN

\section{Adsorption energy prediction from electronic density of states with convolutional neural network}

\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth]{main_fig2_cnn.JPG}
    \caption{\textbf{CNN for Electronic Density of States.}
    a. Kendall rank correlation map illustrating the correlation between adsorption energy
    and some electronic and elementary descriptors.
    Definitions of the notations are provided in Supplementary \cref{si_table15:descriptor_notations}.
    b-c. Architectural of (b)the root and (c)each branch of the CNN model.
    The architecture remains consistent across individual branches.
    d-m. Parity plots demonstrating the performance of the CNN model across nine adsorbates:
    (d)all adsorbates, (e) CO\textsubscript{2}, (f)COOH, (g)CO, (h)CHO, (i) CH\textsubscript{2}O, (j) OCH\textsubscript{3}, (k)O, (l)OH, and (m)H.
    The augmentation data are not displayed in the plots nor included in MAE evaluations.
    Kernel density estimate results are shown along the top and right sides of the main plot,
    representing DFT calculations and CNN model prediction distributions, respectively.}
    \label{main_fig2:cnn_for_eads}
\end{figure}

>>>>

% Results Part One: Adsorption energy prediction from eDOS with CNN

\section{Results}

\subsection{Adsorption energy prediction from electronic density of states with convolutional neural network}

\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth]{main_fig2_cnn.JPG}
    \caption{\textbf{CNN for Electronic Density of States.}
    a. Kendall rank correlation map illustrating the correlation between adsorption energy
    and some electronic and elementary descriptors.
    Definitions of the notations are provided in Supplementary \cref{si_table15:descriptor_notations}.
    b-c. Architectural of (b)the root and (c)each branch of the CNN model.
    The architecture remains consistent across individual branches.
    d-m. Parity plots demonstrating the performance of the CNN model across nine adsorbates:
    (d) all adsorbates, (e) CO\textsubscript{2}, (f)COOH, (g)CO, (h)CHO,
    (i) CH\textsubscript{2}O, (j) OCH\textsubscript{3}, (k)O, (l)OH, and (m)H.
    The augmentation data are not displayed in the plots nor included in MAE evaluations.
    Kernel density estimate results are shown along the top and right sides of the main plot,
    representing DFT calculations and CNN model prediction distributions, respectively.}
    \label{main_fig2:cnn_for_eads}
\end{figure}
